\documentclass{article}
\usepackage[cm]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\usepackage{arev} %% Use option "defaultsans" to use cantarell as sans serif only
\usepackage[T1]{fontenc}
\usepackage[margin=0.5in]{geometry}

\hypersetup{breaklinks=true,%
colorlinks=true,%
linkcolor=cyan,%
urlcolor=MyDarkBlue}

\definecolor{MyDarkBlue}{rgb}{0,0.0,0.45}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\definecolor{contactgray}{gray}{0.3}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%s

\newcommand{\name}[1]{\begin{center}{\LARGE\textbf{#1}}\\\end{center}  \vspace{1pt}}
\newcommand{\program}[1]{\begin{center}\textnormal{#1}\end{center} \vspace{2pt}} 
\newcommand{\contact}[1]{\begin{center}\color{contactgray}{\textnormal{#1}}\end{center} \vspace{2pt}}

\newenvironment{tabbedsection}[1]{
  \begin{list}{}{
      \setlength{\itemsep}{0pt}
      \setlength{\labelsep}{0pt}
      \setlength{\labelwidth}{0pt}
      \setlength{\leftmargin}{0pt}
      \setlength{\rightmargin}{0pt}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\topsep}{#1}
    }
  \item[]
}{\end{list}}

\newenvironment{nospacetabbing}{
    \begin{tabbing}
}{\end{tabbing}\vspace{-1.6pt}}

\newenvironment{resume_header}{}{\vspace{2pt}}


\newenvironment{resume_section}[1]{
  \filbreak
  \vspace{\secsep}
  {\color {MyDarkBlue}\textbf {\underline{#1}}}
  \begin{tabbedsection}{\secsep}
}{\end{tabbedsection}}

\newenvironment{resume_subsection}[2][]{
  \textbf{#2} \hfill {#1}{\parfillskip=0pt\par}
  \begin{tabbedsection}{0.5\secsep}
}{\end{tabbedsection}}

\newenvironment{subitems}{
  \renewcommand{\labelitemi}{-}
  \begin{itemize}
      \setlength{\labelsep}{1em}
}{\end{itemize}}

\newenvironment{resume_employer}[4]{
  \vspace{\secsep}
  \textbf{#1} \\ 
  \textnormal{#2} \hfill {#3 (#4)}{\parfillskip=0pt\par}
  \begin{tabbedsection}{0pt}
  \begin{subitems}
}{\end{subitems}\end{tabbedsection}}


%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Start Document     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{resume_header}
\name{Inesh Loka}
\contact{ineshrloka@gmail.com \hspace{2cm} www.ineshloka.com \hspace{2cm}linkedin.com/in/inesh-l}
\end{resume_header}

\begin{resume_section}{Education}
    \begin{resume_subsection}[Columbus, OH]{The Ohio State University}
      \begin{subitems}
        \item B.S. With Honors, Computer Science and Engineering, Expected December 2025
        \item Cumulative GPA: 3.76
      \end{subitems}
    \end{resume_subsection}
\end{resume_section}

\begin{resume_section}{Work Experience}
  \begin{resume_employer}{London Computer Systems}{Software Development Intern}{Cincinnati, OH}{May 2023 -- August 2023}
    \item Implemented major bug fixes and feature improvements on enterprise-level rental \newline accounting software with over 30,000 corporate clients using C\#, MySQL and AngularJS.
    \item Overhauled financial reporting utilities with improvements in performance and design to facilitate \newline migration to a web-based platform.
    \item Engaged in Agile software development utilizing Gitlab CI, Jira and Confluence for continuous application improvement and collaboration with business analysts and quality assurance engineers.
  \end{resume_employer}
\end{resume_section}

\begin{resume_section}{Leadership}
  \begin{resume_employer}{OSU Artificial Intelligence Club}{Technology Committee Member}{}{September 2022 -- Present}
    \item Assisted 50+ club members in weekly workshops teaching the fundamentals of deep learning with a project based approach.
    \item Created a collection of resources to assist students with deep learning-based projects, including deployment guides using custom APIs and cloud services and implementations of models for various use 
    cases in computer vision, natural language processing and audio signal processing.
    \item Led redesign of the club website using static HTML and CSS to market the club to potential members.
  \end{resume_employer}
\end{resume_section}

\begin{resume_section}{Projects}
  \begin{resume_employer}{Fast Containers}{Linux containers using CLI or GUI}{}{August 2023}
    \item Implemented a lightweight Linux containerization system in C using namespaces and cgroups.
    \item Designed a frontend in Rust using Tauri with effeciency in mind for developers looking to use containers as development environments.
  \end{resume_employer}

  \begin{resume_employer}{Soundbite}{Lightweight audio capture and modification utility for Linux}{}{July 2023}
    \item Built a low-level API for sound capture and manipulation in Rust using CPAL and Hound.
    \item Designed a lightweight GUI using Tauri to allow users to record, play, and modify audio files.
  \end{resume_employer}

  \begin{resume_employer}{Stickerbomb}{Image segmentation artificial intelligence model and web application}{}{May 2023}
    \item Implemented an image segmentation AI model based on UNet using PyTorch to extract subjects from images and generate digital stickers.
    \item Designed a web application to allow users to upload images and generate stickers.
    \item Wrote a blog post detailing the process of creating and deploying the model to AWS.
  \end{resume_employer}

  \begin{resume_employer}{Maze Solver}{Computer vision based maze solver}{}{January 2023}
    \item Implemented a maze solver using computer vision and pathfinding algorithms in Python.
    \item Created a web server using Flask to allow users to upload images of mazes and receive solutions.
  \end{resume_employer}
\end{resume_section}

\begin{resume_section}{Qualifications}
  \begin {nospacetabbing}
      \hspace{2.5cm} \= \kill
      \textbf{Languages} \>C, Python, JavaScript, C\#, Java, C++, Rust, x86 Assembly (AT\&T), Bash, SQL\\* 
      \textbf{Data} \> PyTorch, SciKitLearn, Matplotlib, TensorFlow\\*
      \textbf{Web} \> Django, Flask, React, NextJS, Angular, NodeJS\\*
      \textbf{Desktop} \> Qt, Tauri, Make, .NET WPF, Java Swing\\*
      \textbf{Other} \> Git, MongoDB, MySQL, AWS Lamba, EC2, SageMaker, Google Firebase, Vercel \\*
      \textbf{Courses} \> Software Development \& Design, Low-Level Programming \& Computer Organization, \\
      \> Discrete Structures, Data Structures \& Algorithms, Statistics, Linear Algebra, Calculus
  \end {nospacetabbing}
\end{resume_section}
\end{document}